\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-01-27 papers/jss/article.Rnw
One more comment made by Phillip that I had missed.
Be more specific about how readProtoFiles is automatically called to
read in addressbook.proto on package load, and add a footnote pointing
out that this is why we didn't have to explicitly call readprotofiles
in the example in table1.



git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@865 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

When \CRANpkg{RProtoBuf} is first loaded it calls
\texttt{readProtoFiles} to read in an example \texttt{.proto} file
included with the package.  The \texttt{tutorial.Person} descriptor
and any other descriptors defined in loaded \texttt{.proto} files are
then available on the search path.

>>>>

When \CRANpkg{RProtoBuf} is first loaded it calls
\texttt{readProtoFiles} to read in the example \texttt{addressbook.proto} file
included with the package.  The \texttt{tutorial.Person} descriptor
and all other descriptors defined in the loaded \texttt{.proto} files are
then available on the search path\footnote{This explains why the example in
Table~\ref{tab:proto} lacked an explicit call to
\texttt{readProtoFiles}.}.
